---
title: "shinyloadtest"
author: "Lisa.Anders"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Set working directory to test folder by running below in console: 
# setwd(paste0(getwd(),"/test_slow"))
# setwd(paste0("C:/Users/19796/Documents/Git/Rstudio/demo_app_perf/test_slow_on_connect_workbench"))

```

## Resources 

 - Profiling your shiny app: <https://shiny.rstudio.com/articles/profiling.html> 
 - Shinyloadtest package documentation: <https://rstudio.github.io/shinyloadtest/>
 - Shinyloadtest git repo: <https://github.com/rstudio/shinyloadtest/> 
 - Connect specific article: <https://rstudio.github.io/shinyloadtest/articles/load-testing-authenticated-apps.html>
 - Installing shinycannon: <https://rstudio.github.io/shinyloadtest/articles/shinycannon.html#installation>
 - Analyzing the results: <https://rstudio.github.io/shinyloadtest/articles/analyzing-load-test-logs.html> 

Internal reference: <https://rstudioide.zendesk.com/agent/tickets/86733> and <https://positpbc.atlassian.net/wiki/spaces/PRO/pages/285769868/Novartis+Best+Practices+Call>

## Secret management 

The Connect API key is stored as the r environment variable `connect_api_key`. It can be edited/modified using the usethis package with: 
```r
library(usethis)
usethis::edit_r_environ()
```

## Create "Recording" of a typical user's interaction

Test a single app that has been deployed to Connect. Use the URL from the "open solo" mode on Connect.  
 - Solo mode is important. This URL, when opened with developer options, doesn't work: `https://colorado.posit.co/rsc/connect/#/apps/bec1d4bc-2ab7-4ba3-9bd6-b9e336bf3ff9/access` but this one does: `https://colorado.posit.co/rsc/content/bec1d4bc-2ab7-4ba3-9bd6-b9e336bf3ff9/`

```{r}
library(shinyloadtest)

# Record session
shinyloadtest::record_session(
    target_app_url='https://colorado.posit.co/rsc/content/5f326263-2074-4c73-bc8c-b13c1e84c249',
  connect_api_key=Sys.getenv("CONNECT_API_KEY"))
```

This generates a recording.log file which is the "typical user interacting with the app" which we will use for load testing. 

Alternatively, we can programmatically create the recording using [shinytest2](https://rstudio.github.io/shinytest2/articles/use-application-audit.html?q=load%20test#load-testing-with-shinytest2). 

## Install shinycannnon

Download and install shinycannon: <https://rstudio.github.io/shinyloadtest/articles/shinycannon.html> 

The below is using a windows OS, but can be modified for other OS. 

Test that shinycannon works by calling the help documentation with: 

```bash
cd test_connect_app_upload_file
java -jar shinycannon-1.1.3-dd43f6b.jar -h
```

Set the env variable for the connect api key in your terminal with (note that `set` is used in windows, `export` for mac or linux). Do this in terminal (after adding your API key). 

Windows: 
```bash
set SHINYCANNON_CONNECT_API_KEY=<add your key here>
set SHINYCANNON_CONNECT_URL=<add your content URL here>

set SHINYCANNON_CONNECT_API_KEY=r6xWXQigVVFUAcUPH0mwBnFK6ejt3qpi
set SHINYCANNON_CONNECT_URL=https://colorado.posit.co/rsc/content/e297c186-e1a2-4afe-8abb-3edb52621559


```

Linux: 
```bash
export SHINYCANNON_CONNECT_API_KEY=<add your key here>
export SHINYCANNON_CONNECT_URL=<add your content URL here>
```

Verify that it was set (note that %% is used in windows, $ in linux). 

Windows: 
```bash
echo %SHINYCANNON_CONNECT_API_KEY%
```

Linux:
```bash
echo $SHINYCANNON_CONNECT_API_KEY
```

## Load testing

The load testing will be run either from terminal or from R using the system or system2 commands to pass into the terminal. We will run the load test for simulating the number of simultaneous users, each time saving the results to a different folder. 

Run the load test in terminal: 

Using the URL as a variable (this doesn't work?): 
```bash
java -jar shinycannon-1.1.3-dd43f6b.jar recording.log %SHINYCANNON_CONNECT_URL% --workers 1 --loaded-duration-minutes 2 --output-dir run1 --overwrite-output
```

Change the output directory and number of workers and run it again: 

```bash
java -jar shinycannon-1.1.3-dd43f6b.jar recording.log %SHINYCANNON_CONNECT_URL% --workers 3 --loaded-duration-minutes 2 --output-dir run3 --overwrite-output
```

```bash
java -jar shinycannon-1.1.3-dd43f6b.jar recording.log %SHINYCANNON_CONNECT_URL% --workers 7 --loaded-duration-minutes 2 --output-dir run7 --overwrite-output
```

Providing the URL directly: 

```bash
java -jar shinycannon-1.1.3-dd43f6b.jar recording.log https://colorado.posit.co/rsc/content/5f326263-2074-4c73-bc8c-b13c1e84c249 --workers 1 --loaded-duration-minutes 2 --output-dir run1 --overwrite-output
```

Change the output directory and number of workers and run it again: 

```bash
java -jar shinycannon-1.1.3-dd43f6b.jar recording.log https://colorado.posit.co/rsc/content/5f326263-2074-4c73-bc8c-b13c1e84c249 --workers 3 --loaded-duration-minutes 2 --output-dir run2 --overwrite-output
```

```bash
java -jar shinycannon-1.1.3-dd43f6b.jar recording.log https://colorado.posit.co/rsc/content/5f326263-2074-4c73-bc8c-b13c1e84c249 --workers 7 --loaded-duration-minutes 2 --output-dir run3 --overwrite-output
```

WE can view the availabel shinycannon functions with: 

```bash
java -jar shinycannon-1.1.3-dd43f6b.jar -h
```

Alternatively we could pass in the command from R using the `system()` command (not working): 
Refer to: <https://rstudio.github.io/shinyloadtest/articles/load-testing-authenticated-apps.html#load-testing> 

```{r}
CONNECT_API_KEY <- Sys.getenv("CONNECT_API_KEY")

# "set SHINYCANNON_CONNECT_API_KEY=", #Change this if you are running on Windows
system(
  paste0(
     "export SHINYCANNON_CONNECT_API_KEY=",Sys.getenv("CONNECT_API_KEY")
    )
)

target_url <- "https://colorado.posit.co/rsc/content/5f326263-2074-4c73-bc8c-b13c1e84c249"
workers <- 1
dir <- "run1"

system(
  sprintf(
    "java -jar shinycannon-1.1.3-dd43f6b.jar recording.log %s --workers %s --loaded-duration-minutes 2 --output-dir %s --overwrite-output",
    target_url, workers, dir
  )
)
```

Note that if you are getting a bunch of latency these notes will be useful: 

 - <https://rstudio.github.io/shinyloadtest/articles/limitations-of-shinyloadtest.html>
 - <https://github.com/rstudio/shinyloadtest/issues/121>


## Analyzing the results 

Reference the documentation to understand the different charts: <https://rstudio.github.io/shinyloadtest/articles/analyzing-load-test-logs.html?q=output#report-output> 

```{r}
library(shinyloadtest)
library(dplyr)

df <- load_runs(
  `1 user` = "run1",
  `3 users` = "run2"#,
  #`7 users` = "run3"
)

shinyloadtest_report(df, "report.html")

```

After running this, depending on your organizations security policies, it may help to open as a "preview" rather than in web browser (the error message will be something like "CORS restricted"). It may also be helpful to set self_contained = TRUE, or self_container = FALSE depending on any error messages encountered. 

