---
title: "shinytest2"
author: "Lisa.Anders"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Set working directory to test folder by running below in console: 
# setwd(paste0(getwd(),"/test_auth_apps"))
```

## Resources 

- shinytest2 main documentation: <https://rstudio.github.io/shinytest2/articles/use-application-audit.html#load-testing-with-shinytest2> 
- shinytest2 load testing: <https://rstudio.github.io/shinytest2/articles/use-application-audit.html?q=load%20test#load-testing-with-shinytest2> 
- <https://www.youtube.com/watch?v=Gucwz865aqQ>
- <https://www.youtube.com/watch?v=7KLv6HdIxvU>
- <https://github.com/schloerke/presentation-2022-07-28-rstudioconf22-shinytest2>
- <https://github.com/schloerke/presentation-2022-04-27-appsilon-shinytest2>
- <https://www.jumpingrivers.com/blog/end-to-end-testing-shinytest2-part-1/>


```{r}
library(shinytest2)
library(shinyloadtest)
library(attempt)
library(profvis)
library(ggplot2)
library(shiny)
```


## Profiling 

```{r}
profvis({runApp(appDir = "./test_auth_apps/")})
```










## Shiny testing





Shinyloadtest can use shinytest2 for the recording. This is useful since shinytest2 has a full toolbelt of interaction options and can integrate with CI/CD pipelines. 

## Load testing



Based on the headless instructions, we will use Connect to run our code integrated with shinytest2: <https://rstudio.github.io/shinytest2/articles/use-application-audit.html?q=load%20test#load-testing-with-shinytest2> 


Load some functions: 

```{r}
# Main shiny app
shiny_bg <- function(path, port) {
  options(shiny.port = port)
  shiny::runApp(path)
}

# Start recorder
recorder_bg <- function(port) {
  shinyloadtest::record_session(
    target_app_url = sprintf("http://127.0.0.1:%s", port),
    host = "127.0.0.1",
    port = 8600,
    output_file = "recording.log",
    open_browser = FALSE
  )
}

start_r_bg <- function(fun, path = NULL, port = 3515) {

  # remove NULL elements
  args <- Filter(Negate(is.null), list(path = path, port = port))

  process <- callr::r_bg(
    func = fun,
    args = args,
    stderr= "",
    stdout = ""
  )

  while (any(is.na(pingr::ping_port("127.0.0.1", 3515)))) {
    message("Waiting for Shiny app to start...")
    Sys.sleep(0.1)
  }

  attempt::stop_if_not(
    process$is_alive(),
    msg = "Unable to launch the subprocess"
  )

  process
}

```

Launch the headless app: 

```{r}
target <- start_r_bg(shiny_bg, path = getwd())
# Listening on 127.0.0.1:3515

```

Access it in your browser at 127.0.0.1:3515

Launch the recorder: 

```{r}
recorder <- start_r_bg(recorder_bg)
# Listening on 127.0.0.1:8600

```

Now we have a choice. We can access the app through our browser at 127.0.0.1:8600 and manually simulate typical user interactions in order to get that recording.log file. 

Alternatively we can connect shinytest2 to our hosted application and use it to programmatically simulate interactions from a user for generating the recording.log file. 

Start shinytest2 with a longer load timeout to prevent unecessary errors: 

```{r}
# Start AppDriver with recorder url
# chrome <- shinytest2::AppDriver$new("http://127.0.0.1:8600", load_timeout = 15 * 1000)
chrome <- shinytest2::AppDriver$new("http://127.0.0.1:8600", load_timeout = 50 * 1000)
```

We can now use shinytest2 to programmatically change the inputs without needing manual interaction - super useful if down the road the goal is to be able to progammatically recreate this load test scenario! 

```{r}
chrome$set_inputs(mu = 4, timeout_ = 15 * 1000)

Sys.sleep(1)

chrome$set_inputs(X = .2, timeout_ = 15 * 1000)

Sys.sleep(1)

chrome$set_inputs(Y = 3, timeout_ = 15 * 1000)

Sys.sleep(1)
```


Check the logs: 

```{r}
chrome$get_logs()
```


Close the connection when done. 

```{r}
# clean
chrome$stop()
# needed to avoid
# java.lang.IllegalStateException: last event in log not a
# WS_CLOSE (did you close the tab after recording?)
Sys.sleep(2)

# When you are completely done you will close the app with: 
# target$kill()
```


Now that we have the recording we can use shinycannon to simulate scenarios with multiple users connecting to the application: 

```{r}
target_url <- "http://127.0.0.1:3515"
workers <- 1
dir <- "run1"
system(
  sprintf(
    "java -jar shinycannon-1.1.3-dd43f6b.jar recording.log %s --workers %s --loaded-duration-minutes 2 --output-dir %s",
    target_url, workers, dir
  )
)
```


Now that we are done load testing our app we will close it: 

```{r}
target$kill()
```


## Analyzing the results 

Reference the documentation to understand the different charts: <https://rstudio.github.io/shinyloadtest/articles/analyzing-load-test-logs.html?q=output#report-output> 

```{r}
library(shinyloadtest)
library(dplyr)
library(lubridate)

df <- load_runs(
  `1 user` = "run1",
  `5 users` = "run2",
  `10 users` = "run3"
)

shinyloadtest_report(df, "report.html")

```


## Next level 

Automate the load test with git actions and use as part of a CI/CD pipeline: <https://rstudio.github.io/shinytest2/articles/use-application-audit.html?q=load%20test#automating-with-github-actions>

